\section{Monitoring Regions}
\label{sec:monitoring-regions}

The goal of this library is to inspect the dynamic behavior of a program.
Not only do we want to track statistics about certain quantities or events,
but we also want to know their context.  To model the context of an
observation, we introduce \emph{monitoring regions}.

A monitoring region is not mutable after creation and consequently cannot
capture any data itself.  This job is delegated to an \emph{aggregator}, as
described in section \ref{sec:aggregators}.

\Defclass {monitoring-region}

The base class of all monitoring regions.  Each monitoring operation, i.e.,
each use of \texttt{monitor}, happens in the context of a particular
monitoring region.

\Defmacro {with-monitoring-region} {(name \key{}class \allow{}) \\ \body{} body}

At load-time, create an instance of \textit{class} with the given
\textit{name} and keyword arguments.  Neither \textit{name}, nor the other
arguments are evaluated.  If the keyword argument \textit{class} is not
supplied, it defaults to the class \texttt{monitoring-region}.

At run-time, invoke the forms in \textit{body} in a dynamic environment
where the active region is bound to the previously created monitoring
region instance.

\Defgeneric {monitoring-region-name} {monitoring-region}

The symbol that was supplied as the \textit{name} argument to
\textit{monitoring-region}.

\Defmacro {monitor} {quantity kind}

Call the generic function \texttt{monitor-quantity}.  The symbol
\textit{kind} names a class that is instantiated at load-time and passed to
\texttt{monitor-quantity} as a second argument.  The current region and
current aggregator are passed as third and fourth argument, respectively.

\Defgeneric {monitor-quantity} {quantity kind region aggregator}

Register the data point consisting of \textit{quantity} and \textit{kind}
in the context of \textit{region} in \textit{aggregator}.  The default
method for this function does nothing.

\Defgeneric {enter-monitoring-region} {region aggregator}

This generic function is invoked by \texttt{with-monitoring-region} before
it executes its body.

\Defgeneric {leave-monitoring-region} {region aggregator}

This generic function is invoked by \texttt{with-monitoring-region}
when control is transferred outside of its body.